Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-25 development.tex
Use breakurl package to prevent the bitbucket url from overflowing into the margin.
added matt's changes.
Section 13 edits.

Over time, \enzo's development has followed a trajectory toward
openness.  Started as the graduate research project of Greg Bryan at
the University of Illinois, it was subsequently stewarded by the
Laboratory for Computational Astrophysics (LCA) at the University of
California at San Diego, and has transitioned to a distributed,
completely open, and community-driven project.  Initially, \enzo\ was
versioned using a series of ``snapshots'' of the code base, usually
hand-created by the individuals doing development work.  These were
distributed to collaborators and colleagues, but the central ``trunk''
of development was updated primarily by a single person: while patches
and technology were accepted from external developers, the relatively
small number of individuals using the code resulted in a strong
centralization of development.

As the stewardship of the code passed to the LCA, the code was
released first to ``friendly users'' and then as an open source
release.  However, while the code was made available with
documentation, technology developed in the broader community of users
was typically not re-integrated.  This led to a wide dispersal of
development, largely independent, by individuals who downloaded and
used the version of the code developed by the LCA.

@@

Currently, \enzo\ is developed using the hosted source control
platform Bitbucket (\url{http://bitbucket.org/}) at
\url{http://bitbucket.org/enzo/}.  There are two mailing lists, one
for usage-focused questions and discussion, and another for
development discussion.  Both of these lists are open and publicly
archived.  Bitbucket provides mechanisms for inspecting source code,
hosting branches and forks of the primary source, and for code review.
All proposed source code changes for \enzo\ are subjected to a peer
review process, where experienced developers read, inspect, test, and
provide feedback on source code changes.  All developers, including
long-time \enzo\ contributors and developers, are subject to this
process before their code is included in the primary \enzo\
repository.  By using a remote, hosted system, \enzo\ is now
\textit{completely} open to contributions from the community.
Individuals, who may or may not consider themselves \enzo\ developers,
are free to ``fork'' the \enzo\ code base, develop changes (signed
with their own name), and submit them for review and inclusion.  In
contrast to the centralized, gatekeeper-focused technology used
previously, this enables anyone to contribute changes to be evaluated
for inclusion in the \enzo\ codebase.

>>>>

Over time, \enzo's development has followed a trajectory toward
increasing openness.  Started as the graduate research project of Greg Bryan at
the University of Illinois, it was subsequently stewarded by the
Laboratory for Computational Astrophysics (LCA) at the University of
California at San Diego, and has transitioned to a distributed,
completely open, and community-driven project.  Initially, \enzo\ was
versioned using a series of ``snapshots'' of the code base, usually
hand-created by the individuals doing development work.  These were
distributed to collaborators and colleagues, but the central ``trunk''
of development was updated primarily by a single person: while patches
and technology were accepted from external developers, the relatively
small number of individuals using the code resulted in a strong
centralization of development.

As the stewardship of the code passed to the LCA, the code was
released first to ``friendly users'' and then as a public open source
release.  However, while the code was made available with
documentation, technology developed in the broader community of users
was typically not re-integrated.  This led to a wide dispersal of
development, largely independent, by individuals who downloaded and
used the version of the code developed by the LCA.

@@

Currently, \enzo\ is developed using the hosted source control
platform Bitbucket (\url{http://bitbucket.org/}) at
\url{http://bitbucket.org/enzo/}.  There are two mailing lists, one
for usage-focused questions and discussion, and another for
development discussion.  Both of these lists are open and publicly
archived.  Bitbucket provides mechanisms for inspecting source code,
hosting branches and forks of the primary source, and for code review.
All proposed source code changes for \enzo\ are subjected to a peer
review process, where experienced developers read, inspect, test, and
provide feedback on source code changes.  All developers, including
long-time \enzo\ contributors and developers, are subject to this
process before their code is included in the primary \enzo\
repository.  By using a remote, hosted system, \enzo\ is now
\textit{completely} open to contributions from the community.
Individuals, who may or may not consider themselves \enzo\ developers,
are free to ``fork'' the \enzo\ code base, develop changes (signed
with their own name), and submit them for review and inclusion into
the primary code repository.  In
contrast to the centralized, gatekeeper-focused technology used
previously, this enables anyone to contribute changes to be evaluated
for inclusion in the \enzo\ codebase.  One challenge that this
presents is that the \enzo\ code is a moving target -- to that end, we
recommend that users include the changeset hash of the \enzo\
repository that generated their simulation data (and also the version
of \texttt{yt} used to analyze the data) in their publications.
